Optimal management of a stochastically varying population when policy adjustment is costly

### 2014-06-04 manuscripts/manuscript.Rmd
caching commands must be in a prior chunk.

```{r dependencies, include=FALSE, cache=FALSE}
#source("components/install.R")
```
```{r analysis, include=FALSE}
source("components/analysis.R")
```

@@

```{r Figure_1, fig.cap="Expected net present value by functional form of penalty. Horizontal axis shows the coefficient $c_i$ governing the magnitude of the policy cost, while vertical axis shows fraction of the maximum expected net present value dissipated by the policy cost, $\\tfrac{NPV_0 - NPV_i}{NPV_0}$.  The horizontal line indicates a value of the stock that is reduced by `r reduction * 100`% from the maximum expected value in the absence of policy adjustment costs, $NPV_0({\\bf h_0^*})$. Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.", dependson="quadcosts", fig.width=4, fig.height=3, cache=FALSE}
ggplot(fees, aes(c2, (npv0-value)/npv0, lty=variable)) + 
  geom_line() + 
  geom_hline(aes(yintercept=reduction), linetype=4) + 
  xlab("penalty coefficient") +
  ylab("Reduction in net present value")

@@

<!-- ![image](figure/Figure_6) -->

>>>>

```{r configure, include=FALSE, cache=FALSE}
#source("components/install.R")

library("methods")
library("knitr")
basename <- "manuscript"
opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
               cache.path = paste("components/cache/", basename, "/", sep=""))
opts_chunk$set(cache = 2)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
               comment = NA, verbose = TRUE, echo=FALSE)
# PDF-based figures
opts_chunk$set(dev='pdf')
```

```{r analysis, include=FALSE}
source("components/analysis.R")
```

@@

```{r Figure_1, fig.cap="Expected net present value by functional form of penalty. Horizontal axis shows the coefficient $c_i$ governing the magnitude of the policy cost, while vertical axis shows fraction of the maximum expected net present value dissipated by the policy cost, $\\tfrac{NPV_0 - NPV_i}{NPV_0}$.  The horizontal line indicates a value of the stock that is reduced by `r reduction * 100`% from the maximum expected value in the absence of policy adjustment costs, $NPV_0({\\bf h_0^*})$. Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.", dependson="quadcosts", fig.width=4, fig.height=3}
ggplot(fees, aes(c2, (npv0-value)/npv0, lty=variable)) + 
  geom_line() + 
  geom_hline(aes(yintercept=reduction), linetype=4) + 
  xlab("penalty coefficient") +
  ylab("Reduction in net present value")

@@
